%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Jimmy Callin}{August 27, 1990}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:jimmy.callin@gmail.com}{jimmy@callin.cc}\sbull
\textsmaller{+}46 769 40 30 40 \sbull
Åkerbladsgatan 6\sbull
121 45\thinspace {\large}
Johanneshov\sbull
Sweden

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

%\roottitle{Summary}  % a root section title

\vspace{-0.4em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{A dedicated and light-hearted software developer who loves to get things done and make teams thrive.}

I love taking on big problems head on – nothing is too big to be broken into manageable parts. The less I know about the problem, the more for me to learn.

With me on your team you can expect an optimistic and fun atmosphere along with good forward momentum.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://backlight.co}{Backlight}}
  {\textsc{Stockholm, Sweden}} {%
  \headedsubsection
    {Senior Full-Stack Developer}
    {May. 2021 -- }
{\bodytext{I joined the Academy Award winning \emph{ftrack} working on collaboration tools for the film industry. In January 2023, ftrack merged into Backlight and became part of a global media technology company.

When I started at ftrack, I found a development team with a successful platform with growing pains. Over time I have helped identify and solve several key issues in the product and development process to make sure the product can continue to thrive and scale. 

My role has widely shifted between development infrastructure and product development. In general, I have enjoyed helping our teams thrive by providing the right solutions and processes to tackle hard problems in manageable chunks.

\emph{Key technologies: TypeScript, Python, Docker, React, GitHub Actions, Webpack}}}
}


\headedsection  % sets the header for the section and includes any subsections
  {\href{https://bonniernews.se}{Bonnier News}}
  {\textsc{Stockholm, Sweden}} {%
  \headedsubsection
    {Software Developer \& Lead Developer}
    {Oct. 2017 -- May. 2021}
{\bodytext{I have had the opportunity to help contribute to a diverse set of areas from building editorial tools that streamline workflows of journalists, to reinventing the core backend of one of the most visited news sites in Sweden. In the process I have worked with a large variety of technologies, from web platforms written in React and Javascript, to modern microservice architectures in a Kubernetes environment. I was a key player in finally completing a troubled multi-year project of replacing an old complex monolith CMS with new set of tools built on a modern microservice architecture. 

From Sept. 2020 I became Lead Developer, taking on larger technical strategic projects and lead the cross-team development of a long-term technical backend architecture that significantly reduced the technical debt and better aligned with the organization’s technical vision.

\emph{Key technologies: TDD, Node.js, React, Python, Machine Learning, Elasticsearch, Redis, Kubernetes (Openshift)}
}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://apple.com}{Apple}}
  {\textsc{Cupertino, California}} {%
  \headedsubsection
    {Siri Language Engineer}
    {Mar. 2016 -- Oct. 2016, May 2017 -- Sept. 2017}
{\bodytext{I spent six months in in Cupertino and Paris as a Siri Language Engineering Contractor for the Swedish localization team, working on improving the user experience of the Swedish Siri. Despite my limited time I quickly became an integrated part of the team and took on responsibilities usually reserved for full-time employees. After finishing my Master's thesis I returned for another four months of work.

\emph{Key technologies: Python, Machine Learning, a lot of secret internal tools}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://gavagai.se}{Gavagai}}
  {\textsc{Stockholm, Sweden}} {%
  \headedsubsection
    {Support Manager \& Editor}
    {Jun. 2012 -- Jun. 2015}
    {\bodytext{Gavagai is an AI startup building text analytics tools for customer insights. I was responsible for technical support, where I built a support process that assured customers' technical inquiry were dealt with in a transparent and efficient manner. I also developed several internal tools for data analysis, with work in web development and various natural language processing areas such as sentiment analysis.
    
    \emph{Key technologies: Python, Java, Machine Learning, Regular Expressions}}}
}


\vspace{1em}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Publications}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://aclweb.org/anthology/W15-2508}{Part-of-Speech Driven Cross-Lingual Pronoun Prediction with Feed-Forward Neural Networks.}}
  {\textsc{}} {%
  \headedsubsection
    {Association for Computational Linguistics}
    {Sept. 2015}
    {\bodytext{For some language pairs, pronoun translation is a discourse-driven task which requires information that lies beyond its local context. For cross-lingual pronoun prediction, we suggest a neural network-based model using preceding nouns and determiners as features for suggesting antecedent candidates. Our model scores on par with similar models while having a simpler architecture.}}}


\vspace{1em}

\spacedhrule{-0.2em}{-0.4em}


\roottitle{Education}

\headedsection
  {\href{http://www.uu.se/en/}{Uppsala University}}
  {\textsc{Uppsala, Sweden}} {%

  \headedsubsection
    {Master's and Bachelor's degree in Language Technology}
    {Aug. 2011 -- Apr. 2017}
    {\bodytext{Applying linguistics and computer science for computational modeling of natural language. Elective courses were mainly focused on mathematics and statistics. Master's had a greater focus on research projects.}}

}

\headedsection
  {\href{http://gu.se/english/}{Gothenburg University, Zhejiang University, East China Normal University}}
  {\textsc{Sweden and China}} {%
  \headedsubsection
    {Chinese language and culture}
    {Aug. 2009 -- Jun. 2011} {}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Codes daily in Python and TypeScript. Enjoys CI/CD, TDD, Redis, Elasticsearch, React, Docker, build tools, and learning new technologies}

\vspace{0.5em}
\inlineheadsection
  {Communication skills:}
  {Swedish \emph{(native language)}, English \emph{(full professional proficiency)}.}

\end{document}
